\section*{Experience | \small{Most notable projects}}
{%
  % Next time update CV, I'll write to script to auto-gen below content. Or
  % maybe find another representation.
  \textbf{\event
    {Gee Pacific Technology Services Inc | Philippines}
    {03/2017 - 06/2018}
    {}
  }
  \event
  {Incubation project for new markets}
  {06/2017 - 06/2018}
  {
    - Lead and manage the technical team. \\
    - Define development life circle, system architecture, project structure\\
    - Design the database schema\\
    - Setup Gitlab CI/CD, private Docker registry (using VMWare's Habor) to
    automatically build, test, deploy and, if anything wrong, revert changes.\\
    - Setup production, staging and development environment, include
    configure PostgresSQL SSL, Centos firewall, and Portainer, Nginx\\
    - Work directly with Stake holder for analyzing business requirements\\
    - Work directly with other department (Marketing, HR, Customer Services)
    for hiring, supporting and implement feature request
  }
  \\
  \\
  \event
  {Chinese online E-Commerce projects}
  {03/2017 - 06/2017}
  {
    - Maintain backend applications for old system which was running several
    websites. Occasionally implement new features.\\
    - In first week, I've converted the old project setup from using Eclipse
    and committed jar libraries to Maven, thus, reduced repository size and
    decoupled the source code with the IDE.
  }
  \\
  \\
  \textbf{\event
    {Robert Bosch Engineering Vietnam (RBVH)}
    {07/2014 - 02/2017}
    {}
  }
  \event
  {SureLock App}
  {12/2016  - 02/2017}
  {
    - Develop Android app to flash and upgrade chips firmware via NFC
  }
  \\
  \\
  \event
  {Master Energy Control System (MEC)}
  {11/2016 - 02/2017}
  {
    - MEC is a web interface to monitor and control Bosch boilers system,
    very popular in EU\\
    - Migrate legacy code based on Flexigrid into Bootstrap-table.
    Reduced code size by 25\% (50\% after minification)\\
    - Setup live-reload,  that speed up the development when adding new
    features\\
    - JQuery, Gulp, Nodemon
  }
  \\
  \\
  \event
  {JUP2 Automation Testing | India}
  {04/2016 - 07/2016}
  {
    - The goal is to replace manual test with automation test, which should
    support wide range of productions that communicate to computer via several
    private protocols. Thus, we develop an DSL scripting language and a IDE for
    it to develop, execute scripts, generate reports in HTML, Excel or Markdown
    format.
    \\
    - Implement core libraries to support communication protocols. The previous
    3 year old library (used in manual test) can't  handle extended version of
    the protocol, and there's no document left  after previous developer leave.
    \\
    - Learn Scala in 2 weeks and use ScalaCheck for unit testing core libraries.\\
    - Learn Xtext and Xtend for develop the DSL
  }
  \\
  \\
  \event
  {Internal Server Administration}
  {02/2016 - 02/2017}
  {
    - Set up and maintain an Ubuntu server that runs Jira, Jenkins,
    SVN, Git, Gerrit Code Review and some Tomcat servers.\\
    - Integrate LDAP to Jira, so that Bosch employees can use their internal
    identity to log in. We have serve people of Bosch Vietnam, India and
    German. \\
    - Integrate Jira, Gerrit and Jenkins to support CI/CD.
  }
  \\
  \\
  \event
  {Driving Style Evaluation (DSE)}
  {01/2015 - 07/2015}
  {
    - Build Android app that tracks vehicle statistic (energy, speed, etc),
    analysis and provides suggestions for more effective driving. The app will
    communicate via with specialized Bosch Head Unit via Bluetooth
    \\
    - Convert Matlab algorithm library into a \cpp{} library that's shared
    by both Android (via NDK, JNI) and iOS apps.
  }
}
